Source Code Volatility Metric

### 2020-04-16 paper/article.tex
cite

Most software development projects keep their source code in Git,
which is the de-facto standard in the industry at the moment, or similar
version control systems. Every system, including open
source products like Git, Subversion, and Mercurial, and commerical tools
like Borland StarTeam\texttrademark{} or IBM ClearCase\texttrademark{}
have the same feature: keeping track of the changes
made to the source code files, known as ``logs.''

@@

In order to demonstrate how the metric works we applied it to
\thetotalrepos{} public Java repositories from GitHub and analyzed
its impact on a few other simple metrics, including the number
of files in a repository, the number of directories, and the amount
of bytes.

>>>>

Most software development projects keep their source code in Git~\citet{loeliger2012},
which is the de-facto standard in the industry at the moment, or similar
version control systems. Every system, including open
source products like Git, Subversion, and Mercurial, and commerical tools
like Borland StarTeam\texttrademark{} or IBM ClearCase\texttrademark{}
have the same feature: keeping track of the changes
made to the source code files, known as ``logs.''

@@

In order to demonstrate how the metric works we applied it to
\thetotalrepos{} public Java repositories from GitHub and analyzed
its impact on a few other simple metrics, including the number
of files in a repository, the number of directories, and the amount
of bytes. Since, according to~\citet{muthukumaran2015},
``code change metrics mined from source control repositories have
proven to be the most reliable predictors of bugs in
contemporary software engineering research,'' the introduced volatility
metric may be used to spot maintainability issues.
